---
title: "Redfin-2021-Sale-Data"
author: "ZsuZsuChen"
date: "11/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(rvest)
library(stringr)
library(stringi)
library(tidyverse)
library(dplyr)

```

2021 housing sales data scraped from Redfin.

```{r}
get_sale_info <- function(x){
  h <- read_html(x)
  address <- h %>% html_node(".homeAddress , .dp-subtext") %>% html_text()
  price <- h %>% html_node(".statsValue") %>% html_text() %>% str_replace_all(c("[^[:alnum:]]"=""))
  sqrft <- h %>% html_node(".sqft-section") %>% html_text() %>% str_replace_all(c("[^[:alnum:]]"="", "SqFt"=""))
  bed <- h %>% html_node(".home-main-stats-variant") %>% html_text() %>% str_extract("Price\\d*?Beds") %>% 
    str_replace_all(c("Price"="", "Beds"=""))
  bath <- h %>% html_node(".baths-section") %>% html_text() %>% str_replace("Baths","")
  community <- h %>% html_node(".keyDetailsList, .text-right") %>% html_text() %>% str_extract("Community(.*?)Lot|Community(.*?)MLS") %>%
    str_replace_all(c("Community"="", "Lot"="", "MLS"=""))
  walk <- h %>% html_node(".walkscore") %>% html_text() %>% str_replace_all(" / 100", "")
  tab <- h %>% html_nodes("table") %>% .[2]
  tab <- tab %>% html_table %>% .[[1]] 
  tab <- tab %>% setNames(c("Rating and School", "n students", "Reviews", "Distance"))
  school <-tab[,"Rating and School"]
  school <- school %>% str_replace_all(c("[^[:alnum:]]"="", "Public.*"="", "[:digit:]"=""))
      return(as.data.frame(list("Address"=address, "Sale Price"= price, "Sqr Ft"=sqrft, "Bedrooms"=bed, "Baths"=bath, "Neighborhood"=community,
                       "Walk Score"=walk, "School District" = school)))
}

se1<-get_sale_info("https://www.redfin.com/MA/Boston/81-Waltham-St-02118/unit-4/home/9281055")
se2<-get_sale_info("https://www.redfin.com/MA/Boston/23-Upton-St-02118/unit-3/home/176651583")
se3<-get_sale_info("https://www.redfin.com/MA/Boston/485-Harrison-Ave-02118/unit-204/home/9320601")
se4<-get_sale_info("https://www.redfin.com/MA/Boston/242-Shawmut-Ave-02118/home/17540673")
se5<-get_sale_info("https://www.redfin.com/MA/Boston/66-Appleton-St-02116/unit-2/home/9306592")
dor1<-get_sale_info("https://www.redfin.com/MA/Boston/424-Gallivan-Blvd-02124/home/9102497")
dor2<-get_sale_info("https://www.redfin.com/MA/Boston/6-Ashmont-St-02124/unit-3/home/143295782")
dor3<-get_sale_info("https://www.redfin.com/MA/Dorchester/141-Savin-Hill-Ave-02125/unit-33B/home/177048880")
dor4<-get_sale_info("https://www.redfin.com/MA/Boston/160-Grampian-Way-02125/home/9094226")
dor5<-get_sale_info("https://www.redfin.com/MA/Boston/29-Gibson-St-02122/unit-2L/home/12431828")
rox1<-get_sale_info("https://www.redfin.com/MA/Boston/43-Circuit-St-02119/unit-1/home/9289287")
rox2<-get_sale_info("https://www.redfin.com/MA/Boston/16-Fernboro-St-02121/home/9065030")
rox3<-get_sale_info("https://www.redfin.com/MA/Boston/38-Woodford-St-02125/home/9073499")
rox4<-get_sale_info("https://www.redfin.com/MA/Boston/66-Rockland-St-02119/home/9327360")
rox5<-get_sale_info("https://www.redfin.com/MA/Boston/28-Wabon-St-02121/home/9087602")
jp1<-get_sale_info("https://www.redfin.com/MA/Boston/91-Rossmore-Rd-02130/unit-3/home/45407082")
jp2<-get_sale_info("https://www.redfin.com/MA/Jamaica-Plain/21-Edge-Hill-St-02130/home/9146917")
jp3<-get_sale_info("https://www.redfin.com/MA/Jamaica-Plain/4-Bolster-St-02130/home/9143804")
jp4<-get_sale_info("https://www.redfin.com/MA/Boston/67-Weld-Hill-St-02130/unit-2/home/9139925")
jp5<-get_sale_info("https://www.redfin.com/MA/Boston/18-Boynton-St-02130/unit-2/home/18982912")
ros1<-get_sale_info("https://www.redfin.com/MA/Boston/11-Sherwood-St-02131/unit-1/home/9311516")
ros2<-get_sale_info("https://www.redfin.com/MA/Boston/4625-Washington-St-02131/unit-1/home/176368880")
ros3<-get_sale_info("https://www.redfin.com/MA/Boston/76-Maynard-St-02131/home/9178516")
ros4<-get_sale_info("https://www.redfin.com/MA/Boston/137-Poplar-St-02131/unit-3/home/18995201")
ros5<-get_sale_info("https://www.redfin.com/MA/Boston/67-Weld-Hill-St-02130/unit-2/home/9139925")
sb1<-get_sale_info("https://www.redfin.com/MA/Boston/6-Peters-St-02127/unit-1/home/9302522")
sb2<-get_sale_info("https://www.redfin.com/MA/Boston/720-E-2nd-St-02127/unit-1/home/40274327")
sb3<-get_sale_info("https://www.redfin.com/MA/Boston/406-E-3rd-St-02127/unit-4/home/176339809")
sb4<-get_sale_info("https://www.redfin.com/MA/Boston/181-M-St-02127/home/9192674")
sb5<-get_sale_info("https://www.redfin.com/MA/Boston/17-Thomas-Park-02127/unit-1/home/9318601")
bri1<-get_sale_info("https://www.redfin.com/MA/Boston/1986-Commonwealth-Ave-02135/unit-2/home/9032489")
bri2<-get_sale_info("https://www.redfin.com/MA/Boston/121-Tremont-St-02135/unit-D3/home/9041039")
bri3<-get_sale_info("https://www.redfin.com/MA/Brighton/141-Nottinghill-Rd-02135/unit-1/home/9328721")
bri4<-get_sale_info("https://www.redfin.com/MA/Brighton/55-Brooksdale-Rd-02135/home/9013330")
bri5<-get_sale_info("https://www.redfin.com/MA/Boston/5-Vinal-St-02135/unit-4/home/11508834")
ne1<-get_sale_info("https://www.redfin.com/MA/Boston/43-Commercial-Wharf-02110/unit-6/home/9259439")
ne2<-get_sale_info("https://www.redfin.com/MA/Boston/59-Fleet-St-02109/unit-5/home/9269712")
ne3<-get_sale_info("https://www.redfin.com/MA/Boston/440-Commercial-St-02109/unit-202/home/11838543")
ne4<-get_sale_info("https://www.redfin.com/MA/Boston/371-Hanover-St-02113/unit-5/home/18982985")
ne5<-get_sale_info("https://www.redfin.com/MA/Boston/371-Hanover-St-02113/unit-5/home/18982985")
chr1<-get_sale_info("https://www.redfin.com/MA/Boston/36-Concord-St-02129/unit-2/home/9049086")
chr2<-get_sale_info("https://www.redfin.com/MA/Boston/82-Bunker-Hill-St-02129/unit-82A/home/9062453")
chr3<-get_sale_info("https://www.redfin.com/MA/Charlestown/9-Prospect-St-02129/unit-1/home/107248465")
chr4<-get_sale_info("https://www.redfin.com/MA/Boston/58-High-St-02129/unit-3/home/9061513")
chr5<-get_sale_info("https://www.redfin.com/MA/Charlestown/26-Green-St-02129/home/9062043")
bb1<-get_sale_info("https://www.redfin.com/MA/Boston/382-Commonwealth-Ave-02215/unit-11/home/9271922")
bb2<-get_sale_info("https://www.redfin.com/MA/Boston/43-Commonwealth-Ave-02116/unit-2/home/9252613")
bb3<-get_sale_info("https://www.redfin.com/MA/Boston/350-Marlborough-St-02115/unit-2/home/11836783")
bb4<-get_sale_info("https://www.redfin.com/MA/Boston/483-Beacon-St-02115/unit-36/home/9244007")
bb5<-get_sale_info("https://www.redfin.com/MA/Boston/473-Beacon-St-02115/unit-4/home/9244242")
hp1<-get_sale_info("https://www.redfin.com/MA/Hyde-Park/6-Colchester-St-02136/home/9135129")
hp2<-get_sale_info("https://www.redfin.com/MA/Hyde-Park/935-Metropolitan-Ave-02136/home/9127914")
hp3<-get_sale_info("https://www.redfin.com/MA/Hyde-Park/77-W-Milton-St-02136/home/9134598")
hp4<-get_sale_info("https://www.redfin.com/MA/Boston/1399-River-St-02136/unit-2/home/67978823")
hp5<-get_sale_info("https://www.redfin.com/MA/Hyde-Park/22-Highland-St-02136/home/9129522")
all1<-get_sale_info("https://www.redfin.com/MA/Boston/3-Raymond-St-02134/unit-A/home/8987491")
all2<-get_sale_info("https://www.redfin.com/MA/Boston/50-Hichborn-St-02135/unit-202/home/170710699")
all3<-get_sale_info("https://www.redfin.com/MA/Allston/15-N-Beacon-St-02134/unit-908/home/8988604")
eb1<-get_sale_info("https://www.redfin.com/MA/Boston/335-Maverick-St-02128/unit-1/home/167090092")
eb2<-get_sale_info("https://www.redfin.com/MA/Boston/134-Coleridge-St-02128/home/9110976")
eb3<-get_sale_info("https://www.redfin.com/MA/Boston/439-Chelsea-St-02128/home/9114202")
eb4<-get_sale_info("https://www.redfin.com/MA/Boston/321-Meridian-St-02128/unit-1/home/9314852")
eb5<-get_sale_info("https://www.redfin.com/MA/Boston/276-Princeton-St-02128/unit-3/home/101740384")
chest1<-get_sale_info("https://www.redfin.com/MA/Chestnut-Hill/76-Boylston-St-02467/unit-5/home/11481107")
chest2<-get_sale_info("https://www.redfin.com/MA/Chestnut-Hill/515-Beacon-St-02467/home/11459025")
chest3<-get_sale_info("https://www.redfin.com/MA/Chestnut-Hill/321-Hammond-Pond-Pkwy-02467/unit-307/home/49739693")
chest4<-get_sale_info("https://www.redfin.com/MA/Chestnut-Hill/127-Eliot-St-02467/home/11484319")
chest5<-get_sale_info("https://www.redfin.com/MA/Chestnut-Hill/67-Eliot-St-02467/home/11484435")
wrox1<-get_sale_info("https://www.redfin.com/MA/West-Roxbury/52-Westover-St-02132/unit-52/home/171582109")
wrox2<-get_sale_info("https://www.redfin.com/MA/West-Roxbury/72-74-Manthorne-Rd-02132/unit-0/home/113708114")
wrox3<-get_sale_info("https://www.redfin.com/MA/West-Roxbury/64-Partridge-St-02132/home/9215409")
wrox4<-get_sale_info("https://www.redfin.com/MA/West-Roxbury/1-Salman-St-02132/home/9220384")
wrox5<-get_sale_info("https://www.redfin.com/MA/West-Roxbury/102-Anawan-Ave-02132/home/9208396")
beac1<-get_sale_info("https://www.redfin.com/MA/Boston/73-Revere-St-02114/unit-4/home/9256915")
beac2<-get_sale_info("https://www.redfin.com/MA/Boston/11-Revere-St-02114/unit-3/home/9258369")
beac3<-get_sale_info("https://www.redfin.com/MA/Boston/51-Hancock-St-02114/unit-12B/home/9227983")
beac4<-get_sale_info("https://www.redfin.com/MA/Boston/19-Charles-River-Sq-02114/home/9256309")
beac5<-get_sale_info("https://www.redfin.com/MA/Boston/19-Charles-River-Sq-02114/home/9256309")
fen1<-get_sale_info("https://www.redfin.com/MA/Boston/270-Huntington-Ave-02115/unit-307/home/9234772")
fen2<-get_sale_info("https://www.redfin.com/MA/Boston/1091-Boylston-St-02215/unit-21/home/9275788")
fen3<-get_sale_info("https://www.redfin.com/MA/Boston/1111-Boylston-St-02215/unit-26/home/9240443")
fen4<-get_sale_info("https://www.redfin.com/MA/Boston/70-Fenway-02115/unit-33/home/9265666")
fen5<-get_sale_info("https://www.redfin.com/MA/Boston/137-Peterborough-St-02215/unit-29/home/9242256")
sea1<-get_sale_info("https://www.redfin.com/MA/Boston/133-Seaport-Blvd-02210/unit-1807/home/174425860")
sea2<-get_sale_info("https://www.redfin.com/MA/Boston/135-Seaport-Blvd-02210/unit-1103/home/176367936")
sea3<-get_sale_info("https://www.redfin.com/MA/Boston/135-Seaport-Blvd-02210/unit-3C/home/176643029")
sea4<-get_sale_info("https://www.redfin.com/MA/Boston/135-Seaport-Blvd-02210/unit-1708/home/173087546")
sea5<-get_sale_info("https://www.redfin.com/MA/Boston/133-Seaport-Blvd-02210/unit-2106/home/173087742")
dt1<-get_sale_info("https://www.redfin.com/MA/Boston/1-Franklin-St-02110/unit-1105/home/145254395")
dt2<-get_sale_info("https://www.redfin.com/MA/Boston/121-Portland-St-02114/unit-507/home/165787205")
dt3<-get_sale_info("https://www.redfin.com/MA/Boston/121-Portland-St-02114/unit-704/home/144283659")
dt4<-get_sale_info("https://www.redfin.com/MA/Boston/110-Sudbury-St-02114/unit-4302/home/176672663")
dt5<-get_sale_info("https://www.redfin.com/MA/Boston/210-South-St-02111/unit-43/home/12440287")
ct1<-get_sale_info("https://www.redfin.com/MA/Boston/2-Avery-St-02111/unit-25C/home/11736830")
ct2<-get_sale_info("https://www.redfin.com/MA/Boston/48-Piedmont-St-02116/home/9313401")
ct3<-get_sale_info("https://www.redfin.com/MA/Boston/1-Charles-St-S-02116/unit-707/home/9329859")
ct4<-get_sale_info("https://www.redfin.com/MA/Boston/220-Boylston-St-02116/unit-9001/home/9263371")
ct5<-get_sale_info("https://www.redfin.com/MA/Boston/220-Boylston-St-02116/unit-9013/home/9263397")
matt1<-get_sale_info("https://www.redfin.com/MA/Boston/85-Greenfield-Rd-02126/home/9160601")
matt2<-get_sale_info("https://www.redfin.com/MA/Boston/299-Norfolk-St-02124/home/9080021")
matt3<-get_sale_info("https://www.redfin.com/MA/Mattapan/5-Violet-St-02126/home/9156853")
matt4<-get_sale_info("https://www.redfin.com/MA/Mattapan/5-Violet-St-02126/home/9156853")
matt5<-get_sale_info("https://www.redfin.com/MA/Boston/2-Winston-Rd-02124/home/11835084")
brk1<-get_sale_info("https://www.redfin.com/MA/Brookline/20-Fuller-St-02446/unit-3/home/169937132")
brk2<-get_sale_info("https://www.redfin.com/MA/Brookline/39-St-Paul-St-02446/unit-G1/home/11461572")
brk3<-get_sale_info("https://www.redfin.com/MA/Brookline/101-Dean-Rd-02445/home/11482073")
brk4<-get_sale_info("https://www.redfin.com/MA/Brookline/15-Kendall-St-02445/home/11491142")
brk5<-get_sale_info("https://www.redfin.com/MA/Brookline/330-St-Paul-St-02446/unit-1/home/11442780")
cam1<-get_sale_info("https://www.redfin.com/MA/Cambridge/5-Buckingham-Pl-02138/home/11588231")
cam2<-get_sale_info("https://www.redfin.com/MA/Cambridge/5-Buckingham-Pl-02138/home/11588231")
cam3<-get_sale_info("https://www.redfin.com/MA/Cambridge/250-Brattle-St-02138/unit-21/home/11595098")
cam4<-get_sale_info("https://www.redfin.com/MA/Cambridge/86-Henry-St-02139/unit-3/home/11598909")
cam5<-get_sale_info("https://www.redfin.com/MA/Cambridge/90-Holworthy-St-02138/home/11592718")
som1<-get_sale_info("https://www.redfin.com/MA/Somerville/40-Raymond-Ave-02144/unit-B/home/18906885")
som2<-get_sale_info("https://www.redfin.com/MA/Somerville/31-Adams-St-02145/unit-2/home/17569699")
som3<-get_sale_info("https://www.redfin.com/MA/Somerville/146-W-Adams-St-02144/home/8686407")
som4<-get_sale_info("https://www.redfin.com/MA/Somerville/20-Holyoke-Rd-02144/home/8702689")
som5<-get_sale_info("https://www.redfin.com/MA/Somerville/18-Leland-St-02143/home/8746198")

```

Creating list of names of individual dataframes.

```{r}

df_names <- list(se1,
se2,
se3,
se4,
se5,
dor1,
dor2,
dor3,
dor4,
dor5,
rox1,
rox2,
rox3,
rox4,
rox5,
jp1,
jp2,
jp3,
jp4,
jp5,
se1,
se2,
se3,
se4,
se5,
dor1,
dor2,
dor3,
dor4,
dor5,
rox1,
rox2,
rox3,
rox4,
rox5,
jp1,
jp2,
jp3,
jp4,
jp5,
ros1,
ros2,
ros3,
ros4,
ros5,
sb1,
sb2,
sb3,
sb4,
sb5,
se1,
se2,
se3,
se4,
se5,
dor1,
dor2,
dor3,
dor4,
dor5,
rox1,
rox2,
rox3,
rox4,
rox5,
jp1,
jp2,
jp3,
jp4,
jp5,
ros1,
ros2,
ros3,
ros4,
ros5,
sb1,
sb2,
sb3,
sb4,
sb5,
bri1,
bri2,
bri3,
bri4,
bri5,
ne1,
ne2,
ne3,
ne4,
ne5,
chr1,
chr2,
chr3,
chr4,
chr5,
bb1,
bb2,
bb3,
bb4,
bb5,
hp1,
hp2,
hp3,
hp4,
hp5,
all1,
all2,
all3,
eb1,
eb2,
eb3,
eb4,
eb5,
chest1,
chest2,
chest3,
chest4,
chest5,
wrox1,
wrox2,
wrox3,
wrox4,
wrox5,
beac1,
beac2,
beac3,
beac4,
beac5,
fen1,
fen2,
fen3,
fen4,
fen5,
sea1,
sea2,
sea3,
sea4,
sea5,
dt1,
dt2,
dt3,
dt4,
dt5,
ct1,
ct2,
ct3,
ct4,
ct5,
matt1,
matt2,
matt3,
matt4,
matt5,
brk1,
brk2,
brk3,
brk4,
brk5,
cam1,
cam2,
cam3,
cam4,
cam5,
som1,
som2,
som3,
som4,
som5)
```

Rbind of all seperate housing datafiles into master dataframe.

Data scraped from Redfin of listed recently sold properties stratified by neighborhood.

* Address - property address
* Sale.Price - price sold
* Sqr.Ft - square footage
* Bedrooms - no. bedrooms (NA listed for lofts)
* Baths - no. baths
* Neighborhood
* Walk.Score - numeric score out of 100
* School.District - 6 schools are listed given Boston lottery system

**OF NOTE:** *There are duplicate entries for each individual property becuase 6 different schools are listed for each property. Decision will need to be made if we just want to select the first school listed or do some data wrangling where we group by address.


```{r}
df.2021sales<-do.call("rbind", df_names)

write.csv(df.2021sales, file = "Redfin_2021_SalesData.csv")
```
